Computing Entropies With Nested Sampling

### 2017-07-12 paper/ms.tex
Bracket

To overcome this, NS evolves a population of $N$ particles in the parameter
space towards higher likelihood regions.
The particles are initially initialised from the prior $\pi(\x)$, and the
particle with the lowest likelihood, $L^*_1$, is found and its details are
recorded as output. This worst particle is then discarded
and replaced by a new particle
drawn from the prior $\pi$ but subject to the constraint that its likelihood
must be above $L^*_1$ (this is usually achieved by cloning a surviving particle
and evolving it with MCMC to explore
$\pi(\x)\mathds{1}\left(L(\x) > L^*_1\right)$).
This process is repeated, resulting in an
increasing sequence of likelihoods
\begin{align}
L^*_1, L^*_2, L^*_3,... \label{eqn:likelihood_sequence}
\end{align}
Defining $X(\ell)$ as the amount of prior mass with likelihood greater than
some threshold $\ell$,
\begin{align}
X(\ell) &= \int \pi(\x) \mathds{1}\left(L(\x) > \ell\right) \, d\x,
\end{align}
each discarded point in the sequence can be assigned an $X$-value,
which transforms $Z$ to a one-dimensional integral.
\citet{skilling2006nested}'s key insight was that the
$X$-values of the discarded points are approximately known from the nature of the
algorithm. Specifically, each iteration reduces the prior mass by approximately
a factor $e^{-1/N}$. More accurately, the conditional distribution of
$X_{i}$ given $X_{i-1}$ (and the definition of the algorithm)
is obtainable by letting
$t_i \sim \textnormal{Beta}(N,1)$ and setting $X_{i+1} := t_iX_{i-1}$ (where
$X_1 = t_1$.
The $t_i$ variables represent the proportion of the remaining prior mass
that is {\em retained} at each iteration, after imposing the constraint of the
latest $L^*$ value.

>>>>

To overcome this, NS evolves a population of $N$ particles in the parameter
space towards higher likelihood regions.
The particles are initially initialised from the prior $\pi(\x)$, and the
particle with the lowest likelihood, $L^*_1$, is found and its details are
recorded as output. This worst particle is then discarded
and replaced by a new particle
drawn from the prior $\pi$ but subject to the constraint that its likelihood
must be above $L^*_1$ (this is usually achieved by cloning a surviving particle
and evolving it with MCMC to explore
$\pi(\x)\mathds{1}\left(L(\x) > L^*_1\right)$).
This process is repeated, resulting in an
increasing sequence of likelihoods
\begin{align}
L^*_1, L^*_2, L^*_3,... \label{eqn:likelihood_sequence}
\end{align}
Defining $X(\ell)$ as the amount of prior mass with likelihood greater than
some threshold $\ell$,
\begin{align}
X(\ell) &= \int \pi(\x) \mathds{1}\left(L(\x) > \ell\right) \, d\x,
\end{align}
each discarded point in the sequence can be assigned an $X$-value,
which transforms $Z$ to a one-dimensional integral.
\citet{skilling2006nested}'s key insight was that the
$X$-values of the discarded points are approximately known from the nature of the
algorithm. Specifically, each iteration reduces the prior mass by approximately
a factor $e^{-1/N}$. More accurately, the conditional distribution of
$X_{i}$ given $X_{i-1}$ (and the definition of the algorithm)
is obtainable by letting
$t_i \sim \textnormal{Beta}(N,1)$ and setting $X_{i+1} := t_iX_{i-1}$ (where
$X_1 = t_1$).
The $t_i$ variables represent the proportion of the remaining prior mass
that is {\em retained} at each iteration, after imposing the constraint of the
latest $L^*$ value.
